\documentclass[a4paper,11pt]{scrartcl}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{fullpage}
\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{ifthen}
\usepackage{listings}
\usepackage{color}
\usepackage{hyperref}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{verbatimbox}
\usepackage{float}
\usepackage{subcaption}


\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\lstset{
  language=Python,                  % the language of the code
  basicstyle=\small,                % the size of the fonts that are used for the code
  numbers=left,                     % where to put the line-numbers
  numberstyle=\footnotesize,        % the style that is used for the line-numbers
  stepnumber=2,                     % the step between two line-numbers. If it's 1, each line
                                    % will be numbered
  backgroundcolor=\color{white},    % choose the background color. You must add \usepackage{color}
  showspaces=false,                 % show spaces adding particular underscores
  showstringspaces=false,           % underline spaces within strings
  showtabs=false,                   % show tabs within strings adding particular underscores
  frame=single,                     % adds a frame around the code
  rulecolor=\color{black},          % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. commens (green here))
  tabsize=2,                        % sets default tabsize to 2 spaces
  captionpos=b,                     % sets the caption-position to bottom
  breaklines=true,                  % sets automatic line breaking
  breakatwhitespace=false,          % sets if automatic breaks should only happen at whitespace
  title=\lstname,                   % show the filename of files included with \lstinputlisting;
                                    % also try caption instead of title
  keywordstyle=\color{blue},        % keyword style
  commentstyle=\color{dkgreen},     % comment style
  stringstyle=\color{mauve},        % string literal style
  escapeinside={\%*}{*},           % if you want to add LaTeX within your code
  morekeywords={end,sortrows}       % if you want to add more keywords to the set
}


\begin{document}

\subject{Modeling and Simulation}
\title{Cooking Process Simulation}

\publishers{Supervisor: Martin Bicher}
\author{Martina Mlezivov치, 12306360 - 033 266\footnote{Did the results, introduction and discussion.}\\ % Implemented...
Lana Ram코ak, 12302817 - 033 201\footnote{Added testing permutations and optimized the code, for getting the best order,wrote the implementation and worked on results for the documentation.} \\       % Wrote introduction...
Klaus Derks, 01529340 - 066 926\footnote{Wrote the simulation code of the recipe} \\ % Created the results for...
D치vid Luk치cs, 12306344 - 033 535\footnote{Wrote the json files}} % Collected the data...
\maketitle

\section*{Abstract}

Doing tasks in the right order can be valuable to any kind of process. 
By finding the optimal order one can save time and resources. We were instructed to explore this, particularly in the context of cooking. 
In our Cooking Process Simulation project, we developed a Python model that, when given a recipe, identifies the most efficient task order.
The order is dependand on the number of cooks and available resources.

We tested the model to understand when task order matters and whether 
the quantity of cooks and resources affects the overall duration. Surprisingly, having more than two cooks rarely impacted duration, while a 
different task proved to make a big difference. For cases with only one cook and tasks not dependand on the cook's presence, the order showed minimal importance.

\newpage

\tableofcontents

\newpage

\section{Introduction}

%%%% here we'll include the chapters
\input{chapters/introduction}

\newpage

\section{Model Implementation}
\input{chapters/implementation}

\newpage
\section{Simulation Results}
\input{chapters/simulationresults}

\newpage
\section{Discusion}
\input{chapters/discusion}

\newpage

%\bibliographystyle{plain}
\begin{thebibliography}{1}
  \bibitem{book}
  Cook book. (n.d.). Simply Recipes. Webside: \url{https://www.simplyrecipes.com/dinner-recipes-5091433}.

  \bibitem{asg}
  Cooking Recipe Simulation Assignment. 

  \bibitem{lecture}
  Lectures from subject Modelling and Simulation, version for the academic year 2023/24.
\end{thebibliography}
%\bibliography{References}



\end{document}
